Interactive effects of drought and habitat fragmentation on vital rates of an understory tropical plant

### 2020-12-03 analysis/paper/paper.Rmd
I'm about to re-arrange the introduction

@@

6.  <!--# I'm now thinking this doesn't need to be a separate paragraph, but included in #4.  Need to do some more reading about this though. -->In addition to variation among vital rates, responses to drought and fragmentation could depend on life history stage or plant size. Large established adults could respond differently than seedlings. This is unknown because there are very few systems where we have data on entire life history in a climate change or fragmentation context.

>>>>

    -   "Over 70000 km of new forest edges are being created annually in the Brazilian Amazon by human activities (Broadbent et al., 2008)"

@@

6.  <!--# I'm now thinking this doesn't need to be a separate paragraph, but included in #4.  Need to do some more reading about this though. -->

    In addition to variation among vital rates, responses to drought and fragmentation could depend on life history stage or plant size. Large established adults could respond differently than seedlings. This is unknown because there are very few systems where we have data on entire life history in a climate change or fragmentation context.
